Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-02 submission/figs_largeScale_A.tex
fixed tables refs in figs...

\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_lognorm}
        \label{fig:summary_regressions_A_01}
    }
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_spectralnormlog}
        \label{fig:summary_regressions_A_02}
    }
    \subfigure[ imagenet-1k--ResNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_alpha_weighted}
        \label{fig:summary_regressions_A_03}
    }
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_logpnorm}
        \label{fig:summary_regressions_A_04}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_lognorm}
        \label{fig:summary_regressions_A_05}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_spectralnormlog}
        \label{fig:summary_regressions_A_06}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_alpha_weighted}
        \label{fig:summary_regressions_A_07}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_logpnorm}
        \label{fig:summary_regressions_A_08}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_lognorm}
        \label{fig:summary_regressions_A_09}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_spectralnormlog}
        \label{fig:summary_regressions_A_10}
    }
    \subfigure[ imagenet-1k--PreResNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_alpha_weighted}
        \label{fig:summary_regressions_A_11}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_logpnorm}
        \label{fig:summary_regressions_A_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ResNet; 
             imagenet-1k--EfficientNet; 
             and 
             imagenet-1k--PreResNet; 
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_A}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_lognorm}
        \label{fig:summary_regressions_A_01}
    }
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_spectralnormlog}
        \label{fig:summary_regressions_A_02}
    }
    \subfigure[ imagenet-1k--ResNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_alpha_weighted}
        \label{fig:summary_regressions_A_03}
    }
    \subfigure[ imagenet-1k--ResNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ResNet_logpnorm}
        \label{fig:summary_regressions_A_04}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_lognorm}
        \label{fig:summary_regressions_A_05}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_spectralnormlog}
        \label{fig:summary_regressions_A_06}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_alpha_weighted}
        \label{fig:summary_regressions_A_07}
    }
    \subfigure[ imagenet-1k--EfficientNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_EfficientNet_logpnorm}
        \label{fig:summary_regressions_A_08}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_lognorm}
        \label{fig:summary_regressions_A_09}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_spectralnormlog}
        \label{fig:summary_regressions_A_10}
    }
    \subfigure[ imagenet-1k--PreResNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_alpha_weighted}
        \label{fig:summary_regressions_A_11}
    }
    \subfigure[ imagenet-1k--PreResNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_PreResNet_logpnorm}
        \label{fig:summary_regressions_A_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ResNet; 
             imagenet-1k--EfficientNet; 
             and 
             imagenet-1k--PreResNet; 
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_A}
\end{figure}

### 2021-01-02 submission/figs_largeScale_B.tex
fixed tables refs in figs...

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_lognorm}
        \label{fig:summary_regressions_B_01}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_spectralnormlog}
        \label{fig:summary_regressions_B_02}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_alpha_weighted}
        \label{fig:summary_regressions_B_03}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_logpnorm}
        \label{fig:summary_regressions_B_04}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_lognorm}
        \label{fig:summary_regressions_B_05}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_spectralnormlog}
        \label{fig:summary_regressions_B_06}
    }
    \subfigure[ imagenet-1k--VGG, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_alpha_weighted}
        \label{fig:summary_regressions_B_07}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_logpnorm}
        \label{fig:summary_regressions_B_08}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_lognorm}
        \label{fig:summary_regressions_B_09}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_spectralnormlog}
        \label{fig:summary_regressions_B_10}
    }
    \subfigure[ imagenet-1k--DLA, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_alpha_weighted}
        \label{fig:summary_regressions_B_11}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_logpnorm}
        \label{fig:summary_regressions_B_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ShuffleNet;
             imagenet-1k--VGG;
             and
             imagenet-1k--DLA;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_B}
\end{figure}

>>>>

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_lognorm}
        \label{fig:summary_regressions_B_01}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_spectralnormlog}
        \label{fig:summary_regressions_B_02}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_alpha_weighted}
        \label{fig:summary_regressions_B_03}
    }
    \subfigure[ imagenet-1k--ShuffleNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ShuffleNet_logpnorm}
        \label{fig:summary_regressions_B_04}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_lognorm}
        \label{fig:summary_regressions_B_05}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_spectralnormlog}
        \label{fig:summary_regressions_B_06}
    }
    \subfigure[ imagenet-1k--VGG, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_alpha_weighted}
        \label{fig:summary_regressions_B_07}
    }
    \subfigure[ imagenet-1k--VGG, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_VGG_logpnorm}
        \label{fig:summary_regressions_B_08}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_lognorm}
        \label{fig:summary_regressions_B_09}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_spectralnormlog}
        \label{fig:summary_regressions_B_10}
    }
    \subfigure[ imagenet-1k--DLA, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_alpha_weighted}
        \label{fig:summary_regressions_B_11}
    }
    \subfigure[ imagenet-1k--DLA, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DLA_logpnorm}
        \label{fig:summary_regressions_B_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ShuffleNet;
             imagenet-1k--VGG;
             and
             imagenet-1k--DLA;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_B}
\end{figure}

### 2021-01-02 submission/figs_largeScale_C.tex
fixed tables refs in figs...

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_lognorm}
        \label{fig:summary_regressions_C_01}
    }
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_spectralnormlog}
        \label{fig:summary_regressions_C_02}
    }
    \subfigure[ imagenet-1k--HRNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_alpha_weighted}
        \label{fig:summary_regressions_C_03}
    }
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_logpnorm}
        \label{fig:summary_regressions_C_04}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_lognorm}
        \label{fig:summary_regressions_C_05}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_spectralnormlog}
        \label{fig:summary_regressions_C_06}
    }
    \subfigure[ imagenet-1k--DRN-C, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_alpha_weighted}
        \label{fig:summary_regressions_C_07}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_logpnorm}
        \label{fig:summary_regressions_C_08}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_lognorm}
        \label{fig:summary_regressions_C_09}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_spectralnormlog}
        \label{fig:summary_regressions_C_10}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_alpha_weighted}
        \label{fig:summary_regressions_C_11}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_logpnorm}
        \label{fig:summary_regressions_C_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--HRNet;
             imagenet-1k--DRN-C;
             and
             imagenet-1k--SqueezeNext;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_C}
\end{figure}

>>>>

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_lognorm}
        \label{fig:summary_regressions_C_01}
    }
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_spectralnormlog}
        \label{fig:summary_regressions_C_02}
    }
    \subfigure[ imagenet-1k--HRNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_alpha_weighted}
        \label{fig:summary_regressions_C_03}
    }
    \subfigure[ imagenet-1k--HRNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_HRNet_logpnorm}
        \label{fig:summary_regressions_C_04}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_lognorm}
        \label{fig:summary_regressions_C_05}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_spectralnormlog}
        \label{fig:summary_regressions_C_06}
    }
    \subfigure[ imagenet-1k--DRN-C, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_alpha_weighted}
        \label{fig:summary_regressions_C_07}
    }
    \subfigure[ imagenet-1k--DRN-C, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_DRN_C_logpnorm}
        \label{fig:summary_regressions_C_08}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_lognorm}
        \label{fig:summary_regressions_C_09}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_spectralnormlog}
        \label{fig:summary_regressions_C_10}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_alpha_weighted}
        \label{fig:summary_regressions_C_11}
    }
    \subfigure[ imagenet-1k--SqueezeNext, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNext_logpnorm}
        \label{fig:summary_regressions_C_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--HRNet;
             imagenet-1k--DRN-C;
             and
             imagenet-1k--SqueezeNext;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_C}
\end{figure}

### 2021-01-02 submission/figs_largeScale_D.tex
fixed tables refs in figs...

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_lognorm}
        \label{fig:summary_regressions_D_01}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_spectralnormlog}
        \label{fig:summary_regressions_D_02}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_alpha_weighted}
        \label{fig:summary_regressions_D_03}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_logpnorm}
        \label{fig:summary_regressions_D_04}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_lognorm}
        \label{fig:summary_regressions_D_05}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_spectralnormlog}
        \label{fig:summary_regressions_D_06}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_alpha_weighted}
        \label{fig:summary_regressions_D_07}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_logpnorm}
        \label{fig:summary_regressions_D_08}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_lognorm}
        \label{fig:summary_regressions_D_09}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_spectralnormlog}
        \label{fig:summary_regressions_D_10}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_alpha_weighted}
        \label{fig:summary_regressions_D_11}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_logpnorm}
        \label{fig:summary_regressions_D_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ESPNetv2;
             imagenet-1k--SqueezeNet;
             and
             imagenet-1k--ProxylessNAS;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_D}
\end{figure}

>>>>

 
\begin{figure}[t]
    \centering
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_lognorm}
        \label{fig:summary_regressions_D_01}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_spectralnormlog}
        \label{fig:summary_regressions_D_02}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_alpha_weighted}
        \label{fig:summary_regressions_D_03}
    }
    \subfigure[ imagenet-1k--ESPNetv2, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ESPNetv2_logpnorm}
        \label{fig:summary_regressions_D_04}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_lognorm}
        \label{fig:summary_regressions_D_05}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_spectralnormlog}
        \label{fig:summary_regressions_D_06}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_alpha_weighted}
        \label{fig:summary_regressions_D_07}
    }
    \subfigure[ imagenet-1k--SqueezeNet, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_SqueezeNet_logpnorm}
        \label{fig:summary_regressions_D_08}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert_{F}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_lognorm}
        \label{fig:summary_regressions_D_09}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_spectralnormlog}
        \label{fig:summary_regressions_D_10}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\hat{\alpha}$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_alpha_weighted}
        \label{fig:summary_regressions_D_11}
    }
    \subfigure[ imagenet-1k--ProxylessNAS, $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ ]{
        \includegraphics[width=3.7cm]{img/omsr_imagenet_1k_ProxylessNAS_logpnorm}
        \label{fig:summary_regressions_D_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k--ESPNetv2;
             imagenet-1k--SqueezeNet;
             and
             imagenet-1k--ProxylessNAS;
             repsectively.
             Each column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; 
             and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$;
             repsectively.
            }
    \label{fig:summary_regressions_D}
\end{figure}
